Figure 2c

### 2018-02-12 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
fixing some rmd typos
removing violin and updating name to lncTAM34a for p1_hct116_hek293t

*For a schematic representation of the P1 construct please see Figure 2c.

@@

#fix gene labels
data <- data %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
    TRUE ~ "somehow missed a gene"
  ))

stats <- stats %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
    TRUE ~ "somehow missed a gene"
  ))

vl <- vl %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
    TRUE ~ "somehow missed a gene"
  ))

@@

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = construct,
      y = logValue,
      group = interaction(construct, plotGene)
    ),
    trim = TRUE,
    alpha = 0.3,
    fill = "gray",
    color = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = construct,
      y = logValue,
      fill = plotGene
    ),
    binwidth = 1/10,
    #alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 3,
    show.legend = TRUE
  ) +
  facet_grid(. ~ `Cell line`) +
  labs(
    x = "Construct",
    y = "log2 activity (a.u.)"
  )

>>>>

*For a schematic representation of the P1 construct please see Figure 2-Supplement 1a-b.

@@

#fix gene labels
data <- data %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
    TRUE ~ "somehow missed a gene"
  ))

stats <- stats %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
    TRUE ~ "somehow missed a gene"
  ))

vl <- vl %>%
  mutate(plotGene = case_when(
    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
    TRUE ~ "somehow missed a gene"
  ))

@@

p <- ggplot(data = NULL) +
  geom_dotplot(
    data = data, 
    aes(
      x = construct,
      y = logValue,
      fill = plotGene
    ),
    binwidth = 1/10,
    #alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 3,
    show.legend = TRUE
  ) +
  facet_grid(. ~ `Cell line`) +
  labs(
    x = "Construct",
    y = "log2 activity (a.u.)"
  )
